---
title: "Case_Study2"
author: "Chao Li"
date: "Updated on: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    self_contained: yes
    number_sections: True
    theme: cosmo
    toc: True
  pdf_document:
    number_sections: True
  always_allow_html: true
---


```{r include=FALSE}
pacman::p_load(tidyverse, ggplot2,kableExtra)
```


```{r include=FALSE}
data <- read.csv('data/casestudy.csv',row.names = 1)
data %>% glimpse() 
```

# Required Information

## Total revenue for the current year
```{r echo=FALSE}
data %>% group_by(year) %>% summarise(Total_y = sum(net_revenue)) %>%   kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```

## New Customer Revenue 
```{r echo=FALSE}
df = data%>% 
  pivot_wider(names_from = year,values_from = net_revenue) %>% 
  mutate(new2016 = if_else(is.na(`2015`)&(!is.na(`2016`)),1,0),
         new2017 = if_else(is.na(`2016`)&(!is.na(`2017`)),1,0)) 
  
new.2016 <- df %>% filter(new2016 == 1) %>% summarise(new_2016 = sum(`2016`))
new.2017 <- df %>% filter(new2017 == 1) %>% summarise(new_2017 = sum(`2017`))
cbind(new.2016,new.2017) %>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```

## Existing Customer Growth.

```{r echo=FALSE}
df <- df%>% 
  mutate(exist2016 = if_else(!is.na(`2015`)&(!is.na(`2016`)),1,0),
         exist2017 = if_else(!is.na(`2016`)&(!is.na(`2017`)),1,0)) 

growth.2016 <- df %>% 
  filter(exist2016 == 1) %>% 
  summarise(growth_2016 = sum(`2016`)-sum(`2015`))

growth.2017 <- df %>% 
  filter(exist2017 == 1) %>% 
  summarise(growth_2017 = sum(`2017`)-sum(`2016`))

cbind(growth.2016,growth.2017) %>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```

## Revenue lost from attrition
```{r echo=FALSE}
df <- df%>% 
  mutate(lost2016 = if_else(!is.na(`2015`)&(is.na(`2016`)),1,0),
         lost2017 = if_else(!is.na(`2016`)&(is.na(`2017`)),1,0)) 

lost.2016 <-df %>% 
  filter(lost2016 == 1) %>% 
  summarise(lost2016 = sum(`2015`))

lost.2017 <- df %>% 
  filter(lost2017 == 1) %>% 
  summarise(lost2017 = sum(`2016`))

cbind(lost.2016,lost.2017) %>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```

## Existing Customer Revenue Current Year
```{r echo=FALSE}
y2016 <- df %>% 
  filter(exist2016 == 1) %>% 
  summarise(`2016` = sum(`2016`))
row.names(y2016) <- 'Revenue'

y2017 <- df %>% 
  filter(exist2017 == 1) %>% 
  summarise(`2017` = sum(`2017`)) 
row.names(y2017) <- 'Revenue'

cbind(y2016,y2017) %>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```
##	Existing Customer Revenue Prior Year

```{r echo=FALSE}
y2016 <- df %>% 
  filter(exist2016 == 1) %>% 
  summarise(`2016` = sum(`2015`))
row.names(y2016) <- 'Revenue'

y2017 <- df %>% 
  filter(exist2017 == 1) %>% 
  summarise(`2017` = sum(`2016`)) 
row.names(y2017) <- 'Revenue'

cbind(y2016,y2017) %>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```
## Total Customers Current Year

```{r echo=FALSE}
data %>% group_by(year) %>% summarise(Count = length(unique(customer_email))) %>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```
## Total Customers Previous Year

This result is same as the previous one

```{r echo=FALSE}
data %>% group_by(year) %>% summarise(Count = length(unique(customer_email))) %>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```
## New Customers

The following table only shows 5 customers of each year

```{r echo=FALSE}
y2016 <- df %>% filter(new2016 == 1) %>% select(customer_email)
colnames(y2016) <- '2016'

y2017 <- df %>% filter(new2017 == 1) %>% select(customer_email)
colnames(y2017) <- '2017'
  
cbind(y2016[1:5,],y2017[1:5,])%>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```
##	Lost Customers

The following table only shows 5 customers of each year

```{r echo=FALSE}
y2016 <- df %>% filter(lost2016 == 1) %>% select(customer_email)
colnames(y2016) <- '2016'

y2017 <- df %>% filter(lost2017 == 1) %>% select(customer_email)
colnames(y2017) <- '2017'
  
cbind(y2016[1:5,],y2017[1:5,])%>% kable() %>% 
  kable_styling(bootstrap_options='striped',full_width=F,position = 'center')
```

# Visualization

## Total revenue of each year

```{r echo=FALSE}
data %>% 
  group_by(year) %>% 
  summarise(Total_revenue = sum(net_revenue)) %>% 
  ggplot(aes(x = year,y = Total_revenue))+
  geom_bar(stat = "identity")+
  labs(title = 'Total revenue of each year')
```

The revenue in 2016 is lower than other years.

## Total revenue of each year

```{r echo=FALSE}
data %>% mutate(year = as.character(year)) %>% 
  ggplot(aes(x = year,y = net_revenue, fill = year))+
  geom_boxplot()+
  labs(title = 'Box plot of revenue in each year')
```

All three years has similar revenue structure where they have same customer revenue distribution.


